---
title: "P8105_hw6_zc2555"
author: "Ziyu Chen"
date: "12/4/2021"
output: github_document
---

# r set up, lodaing packages 
```{r}
library(tidyverse)
library(modelr)

```


# Problem 1, Clean the dataset, recode certain variables into factors

* As we can see that variables: babyset, frace, malform, mrace are categorical data so we need to tranform them into factors.
```{r}
birthweight_df = 
  read_csv("data/birthweight.csv") %>%
  janitor::clean_names() %>%
  mutate(
    babysex = recode_factor(
      as_factor(babysex), 
      "1" = "male",
      "2" = "female"),
    frace = recode_factor(
      as_factor(frace), 
      "1" = "White", 
      "2" = "Black", 
      "3" = "Asian", 
      "4" = "Puerto Rican", 
      "8" = "Other", 
      "9" = "Unknown"),
     malform = recode_factor(
       as_factor(malform), 
       "1" = "present", 
       "0" = "absent"),
     mrace = recode_factor(
       as_factor(mrace), 
       "1" = "White", 
       "2" = "Black", 
       "3" = "Asian", 
       "4" = "Puerto Rican", 
       "8" = "Other"))
  
```

Check if there are any missing data
```{r message = FALSE}
map(birthweight_df, ~sum(is.na(.)))
```

The birth_df is the cleaned dataset. 

* Fit a regression model 

Since the outcome variable is birthweight, we might be interested in looking at baby's sex and it's head circumference as well as it's length at birth. We also want to see the parental effect like father and mother's races and mother's height on baby's weight. 

```{r}
fit <- lm(bwt ~ babysex + bhead + blength + mheight + gaweeks + mrace + frace, data = birthweight_df)

fit %>% broom::tidy()
```


```{r}
birthweight_df %>%
  modelr::add_residuals(fit) %>% 
  modelr::add_predictions(fit) %>% 
  ggplot(aes(x = pred, y = resid)) +
  geom_point()
```
From the diagnostic, we can see that although there are several residual points that are not optimal, the overall model still looks good.




* Compare the models
One using length at birth and gestational age as predictors (main effects only)

```{r}
model_1 <- lm(bwt ~ blength + gaweeks, data = birthweight_df)

model_1 %>% broom::tidy()
```
One using head circumference, length, sex, and all interactions (including the three-way interaction) between these (Since length at birth and gestational age are main effects, we also include gestational age in our model.)

```{r}
model_2 <- lm(bwt ~ bhead + blength + babysex + bhead*blength + blength*babysex + bhead*babysex + bhead*blength*babysex, data= birthweight_df)

model_2 %>% broom::tidy()
```

* Cross Validation

```{r}
Cross_validation = crossv_mc(birthweight_df, 100)

  Cross_validation %>% 
  mutate(
    train = map(train, as_tibble),
    test = map(test, as_tibble)
  )

Cross_validation = Cross_validation %>%
  mutate(
    p1_fit = map(train, ~lm(bwt ~ babysex + bhead + blength + wtgain + mheight, data = .x)), 
    model1 = map(train, ~lm(bwt ~ blength + gaweeks, data = .x)), 
    model2 = map(train, ~lm(bwt ~ bhead + blength + babysex + bhead*blength + blength*babysex + bhead*babysex + bhead*blength*babysex, data = .x))
  ) %>%
  mutate(
    rmse_p1fit = map2_dbl(p1_fit, test, ~rmse(model = .x, data = .y)),
    rmse_model1 = map2_dbl(model1, test, ~rmse(model = .x, data = .y)),
    rmse_model2 = map2_dbl(model2, test, ~rmse(model = .x, data = .y)))
```

Fitting the plots

```{r}
Cross_validation %>% 
  select(starts_with("rmse")) %>% 
  pivot_longer(
    everything(),
    names_to = "model", 
    values_to = "rmse",
    names_prefix = "rmse_") %>% 
  mutate(model = fct_inorder(model)) %>% 
  ggplot(aes(x = model, y = rmse, fill = model)) + 
  geom_violin(alpha = 0.3) +
  labs(
    title = "Violin plot for RMSE across three models", 
    x = "model", 
    y = "RMSE"
  )
```





# Problem 2


```{r}
weather_df = 
  rnoaa::meteo_pull_monitors(
    c("USW00094728"),
    var = c("PRCP", "TMIN", "TMAX"), 
    date_min = "2017-01-01",
    date_max = "2017-12-31") %>%
  mutate(
    name = recode(id, USW00094728 = "CentralPark_NY"),
    tmin = tmin / 10,
    tmax = tmax / 10) %>%
  select(name, id, everything())
```
